---
title: "Business Analytics Assignment1"
author: "Jyoti Phogat"
output: pdf_document
date: "2022-09-25"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Install the ISLR library using the install.packages() command
```{r}
install.packages("ISLR")
library(ISLR)
```

```{r}
install.packages("knitr") 
library(knitr) 
install.packages("tinytex") 
tinytex::install_tinytex(force=TRUE) 
```
## importinmg carseats dataset
```{r}
library(ISLR)
CarseatsData<-Carseats
summary(CarseatsData)
```
## Carseat dataset has 400 observations and 11 variables

```{r}
str(CarseatsData)
```
## Maximum value of avertising attribute is 29.000
```{r}
summary(CarseatsData$Advertising)
```

## IQR of Price Attribute
```{r}
IQR(CarseatsData$Price)
```

##Plot between Sales and Price
```{r}
plot(CarseatsData$Sales, CarseatsData$Price, main="Scatter plot and linear fit between Sales and Price", xlab = "Sales",ylab = "Price")
```

## correlation of Price and sales
```{r}
library(dplyr)
cor(select(CarseatsData,1,6))
```
## The corelation coefficient values above suggest there is weak negative linear corelation between both the attributes.


